\documentclass[a4paper,12pt]{article}
\input{commons/preamble}
\geometry{
    paper=a4paper,
    top=0.5cm,
    bottom=2cm,
    left=2cm,
    right=2cm,
    headheight=0.75cm,
    footskip=1.5cm,
    headsep=0.75cm,
}

\newcommand{\linker}[1]{\colorbox{yellow}{#1}}

\begin{document}
    {\footnotesize Ilyin Vladimir, 3530901/10005}
    \hfill
    {\footnotesize Linkers: 10, Total: 516 words.}

    \begin{center}
        {\Large Cryptocurrencies}
    \end{center}
    
    \normalfont
    \textbf{Outline:}
    \begin{itemize}
        \item[I.] Cryptocurrency is a safe payment method.
        \item[II.] Security of transactions.
        \begin{itemize}
            \item[A.] Blockchain.
            \item[B.] Anonymity.
        \end{itemize}
        \item[III.] A replacement of traditional money.
        \begin{itemize}
            \item[A.] Fast \& seamless transactions.
            \item[B.] Government independency.
            \item[C.] Investment potential.
        \end{itemize}
        \item[IV.] Cryptocurrencies are the secure future of banking system and businesses should be using it more.
    \end{itemize}
    \vspace{1cm}
    \setlength{\parindent}{20pt}

    % Введение (I)
    Cryptocurrency (or crypto) is one of the most popular, yet commonly mistaken, concepts of 21st century.
    Most people who are not familiar with this technology are afraid of it, even among younger generations.
    Unlike their expectations, \linker{in reality}, crypto is a safe payment method, which is widely reffered as the
    future of the banking system.

    % Основная часть (II & III)
    \linker{Firstly}, crypto transactions are secure and independent from each other. This is achieved by usage of
    another technology called 'blockchain'. \linker{In short}, this kind of structure allows for complete independency
    of 'blocks'. In crypto case, each block contains several transactions that happened in the same two minutes.
    After two minutes, another block, which has a pointer to the previous block, will be created for future transactions.
    \linker{Another good reason} for securiy of crypto is its anonymity. \linker{Although}, \linker{in fact}, most of the cryptocurrencies aren't
    anonymous. \linker{Instead}, they are pseudo-anonymous, or replacing your name with a fake one. \linker{However}, instead of everybody
    going by the name 'John Smith' or something along those lines, your name is replaced with the numbers and digits of
    your wallet address. A wallet is where your crypto is stored. It's a digital space that only people with the address and
    the access keys can get to and move the contents around. However, it's also what make crypto identifiable, since a wallet's
    address is kept on a cryptocurrency's blockchain.

    \linker{Secondly}, cryptocurrency is possibly the future replacement of traditional money. Crypto was essentially designed to be used
    in the internet which implies that all transactions are as fast as your internet connections speed and as seamless as pressing
    a couple buttons in your smartphone. With modern banking mobile applications money transferring was also made easy, yet you
    can't really send out your russian roubles to USA. This leads to the second point. Cryptocurrency is decentralized and isn't controlled
    by any authority. This means that you can't be banned from using crypto, or your money can't be frozen to restrain you.
    No matter what happens, your money will remain secure. \linker{Another point is} the investment potential of cryptocurrencies. Each second
    most of the cryptocurrencies change their stock value (apart from cryptocurrencies pegged to normal currencies, such as USDT). There are
    two basic approaches with which you can invest in crypto. One approach is to buy and hold something like Bitcoin, which has gone from
    virtually worthless in 2008 to thousands of dollars a coin today. Another would be a more active strategy, buying and selling
    cryptocurrencies that experience volatility.

    % Заключение (IV)
    \linker{To sum up}, cryptocurrencies are believed to be the secure future of banking system. It is safe, fast and independent from
    outer factors, such as politics. Although it is not that convenient to pay with crypto in shops right now, businesses should
    definitely consider using it more.
\end{document}